% Copyright (C) 2017 Daniel Page <dan@phoo.org>
%
% Use of this source code is restricted per the CC BY-SA license, a copy of
% which can be found via http://creativecommons.org (and should be included 
% as LICENSE.txt within the associated archive or repository).

% =============================================================================

\leveldown{Background}

Imagine you own a cryptographic accelerator, denoted $\PARTY{T}$: it is used
as a low-cost HSM in your data center, supporting secure key generation and 
storage plus off-load of various cryptographic operations via a standardised 
protocol (or API).
\DESCINTRO[none]
{a scalar}
{an  input point}
{i.e., multiplies the input point by the scalar}
{an output point}
Although it currently functions correctly, an electrical fault demands that
$\PARTY{T}$ 
is replaced.  However, doing so presents a serious problem: the API cannot 
be used to export 
$\PRI{\CHAL{k}}$, 
so a replacement will have to be generated and used thereafter.  This means 
compatibility with existing data sets will be lost, {\em unless} 
$\PRI{\CHAL{k}}$ 
itself can be recovered by some other means.

% -----------------------------------------------------------------------------

\levelstay{Material}

\leveldown{\lstinline[language={bash}]|\$\{ARCHIVE\}/CONF(ARCHIVE_PATH,CID)/\$\{USER\}.T|}

\DESCMATERIALT{%
\item $\PUB{P_x}$,
      the $x$-coordinate of elliptic curve point $\PUB{P} = \TUPLE{ \PUB{P_x}, \PUB{P_y} }$
      (represented as a                   hexadecimal integer string),
      and
\item $\PUB{P_y}$,
      the $y$-coordinate of elliptic curve point $\PUB{P} = \TUPLE{ \PUB{P_x}, \PUB{P_y} }$
      (represented as a                   hexadecimal integer string),
}{%
\item $\PUB{Q_x}$,
      the $x$-coordinate of elliptic curve point $\PUB{Q} = \TUPLE{ \PUB{Q_x}, \PUB{Q_y} } = \PMUL{\PRI{\CHAL{k}}}{\PUB{P}}$
      (represented as a                   hexadecimal integer string),
      and
\item $\PUB{Q_y}$,
      the $y$-coordinate of elliptic curve point $\PUB{Q} = \TUPLE{ \PUB{Q_x}, \PUB{Q_y} } = \PMUL{\PRI{\CHAL{k}}}{\PUB{P}}$
      (represented as a                   hexadecimal integer string),
}%
Note that:

\begin{itemize}
\item $\PARTY{T}$ 
      uses an left-to-right binary scalar multiplication
      (i.e., an additive analogue of~\cite[Section 2.1]{SCALE:Gordon:85}) 
      to compute 
      $
      \PUB{Q} = \PMUL{\PRI{\CHAL{k}}}{\PUB{P}} .
      $
      In doing so, it assumes use of the
      \IfStrEqCase{CONF(CURVE,CID)}{%
        {0}{NIST-P-192 }% NIST-P-192
        {1}{NIST-P-224 }% NIST-P-224
        {2}{NIST-P-256 }% NIST-P-256
        {3}{NIST-P-384 }% NIST-P-384
        {4}{NIST-P-521 }% NIST-P-521
      } elliptic curve
      \[
      E( \DOM{\B{F}_p} ) : y^2 = x^3 + \DOM{a_4} x + \DOM{a_6}
      \]
      for standardised~\cite{SCALE:FIPS:186:00} domain parameters 
      $\DOM{p}$, 
      $\DOM{a_4}$, 
      and 
      $\DOM{a_6}$.
\item More concretely, 
      $\PARTY{T}$ 
      uses OpenSSL to support arithmetic on the elliptic curve.  You can 
      browse the associated source code at
      \[
      \mbox{\url{http://github.com/openssl}}
      \]
      noting that the choice outlined above implies use of 
      \lstinline[language={C}]{ec_GFp_simple_add}
      and
      \lstinline[language={C}]{ec_GFp_simple_dbl}
      to realise the (additive) group operation, i.e., to compute either a
      point addition or doubling, within the scalar multiplication.
\item Crucially, 
      $\PARTY{T}$ 
      applies {\em no} checks to either the input or output points (e.g., to check whether $\PUB{P} \in E( \DOM{\B{F}_p} )$ and reject $\PUB{P}$ if not).
\item At least from a Mathematical point of view, there is no valid affine 
      representation of the point at infinity.  If computation of
      $
      \PMUL{\PRI{\CHAL{k}}}{\PUB{P}}
      $
      does yield the point at infinity, 
      $\PARTY{T}$ 
      therefore signals this fact by producing
      \[
      \PUB{Q} = \TUPLE{ \PUB{Q_x}, \PUB{Q_y} } = \TUPLE{ 0, 0 }
      \]
      as output (rather than some special-purpose mechanism, e.g., an error or an alternative output format).
\end{itemize}

% -----------------------------------------------------------------------------

\levelup{Tasks}

\begin{enumerate}
\item \DESCTASKIMPL
      {$\PRI{\CHAL{k}}$}
      {\mbox{\lstinline[language={bash}]|./attack \$\{USER\}.T|}}
\item \DESCTASKEXAM
      {\mbox{\lstinline[language={bash}]|\$\{ARCHIVE\}/CONF(ARCHIVE_PATH,CID)/\$\{USER\}.exam|}}
\end{enumerate}

% =============================================================================
